---
title: "Exploratory"
author: "MD"
date: "February 12, 2015"
output: html_document
---
Read all the records
```{r}
setwd("../Data")
datafem<-read.csv("fem_todos_.csv",sep=";")
datamasc<-read.csv("masc_todos_.csv",sep=";")
head(datafem)
```

It is important to notice that the comma is used instead of the decimal point in the columns bmi,SBP, and DBP so it is important to convert to the appropiate character.
```{r}
summary(datafem)
str(datafem)
summary(datamasc)
str(datamasc)
homoname<-names(datafem)
homoname[10]<-"hyper"
names(datafem)<-homoname
datall<-rbind(datafem,datamasc)
datall$bmi<-as.numeric(datall$bmi)
datall$SBP<-as.numeric(datall$SBP)
datall$DBP<-as.numeric(datall$DBP)
datall$DBP<-as.factor(round(datall$DBP))
datall$bmi<-as.factor(round(datall$bmi))
library(caret)
nzv<-nearZeroVar(datall,saveMetrics=TRUE)
```

With this information I noticed that the data is clean and doesn't include NA or missing information.
I decided to merge the information of men and women and homegeneize the name of the columns.
The objective is to predict the systolic BP. The near zero values show that all the variables are meaningful for prediction

```{r}
set.seed(1000)
indx<-createDataPartition(y=datall$SBP,p=0.7,list=FALSE)
trainingM<-datall[indx,]
testingM<-datall[-indx,]
```
Fit a model using random forest to predict SBP base on Age bmi and Diastolic BP.
```{r}
set.seed(1000)
modfit2<-train(SBP ~ Age + bmi+ DBP,method="rf",prox=TRUE,data=trainingM,ntree=15)
Ptest2<-predict(modfit2,testingM)
predvec<-testingM[1,]
predvec$Age<-50
predvec$bmi<-30
predvec$DBP<-90
predvec$bmi<-as.factor(predvec$bmi)
predvec$DBP<-as.factor(predvec$DBP)
pres<-predict(modfit2,predvec)
print (pres)
```

